\documentclass{book}
\title{Untitled cyberpunk thing}
\author{Not **** *******}

\begin{document}
\pagenumbering{gobble}
\maketitle
\chapter{''The Wired''}

The World began to melt away. Hypnagogic images danced eerily around the insides of Bud's eyes, neurons firing in the darkness created by his closed eyes, leaving surreal patterned flashes of purple in their wake. Seconds passed. In the distance Bud could hear the sound of drives and fans spinning up, his computer loading into RAM the required programs to project his mind into a false world. He braced for it, waiting for the inevitable jolt as his mind left the confines of physical reality. Pin pricks of light appeared in the darkness, dots of digital seeping into his grey matter. And then it began. A feeling of falling at speeds far greater than any human body could survive, blood rushing through his ears drowning out every other sound, garbled audio playing in his mind, snapshots of memories, pictures and surreal lightshows. Finally, there was white.

The white slowly faded into colours, sounds, and textures. The Wired, a fusion of the mental and the digital. A virtual world experienced by immersing one's consciousness in digital sensations. It was a distributed network that created digital signals, sent from a server into images, sounds, sensations, that your brain could understand through the Neuro-Network Protocol, a two way system, your brain would also send back signals to the network in order to control your virtual body. The result, is a massive interactive computerised dream.

There are millions of servers running the Neuro-Network Protocol, all interconnected, forming a digital universe with every experience known to man. The Protocol (NNP) works by using your brain as a processor to visualise the digital reality, connecting you to a massive online simulation, in which your consciousness would be free to interact, do business, play games, socialise, and even work.

All the Wired required for use was a Neuro-Translator. The device that facilitated unfettered communication between your mind and the digital world. It was an impressive piece of technology. The translator took a week to calibrate itself to a users mental language using limited artificial intelligence, forming an understanding between the fleshy computational organ and it's metal counterpart. A truly miraculous piece of technology.

It took two years from the invention of the Wired to become the prime platform for human communication. Subcultures, friendships, loves, formed burned and replaced by the minute within the Wired's endless digitized depth. Bud had a taste for the Wired. The ``true'' Wired that is. Like most nihilistic disenfranchised wire jockies, Bud held a disdain for the consumer Wired and it's hoard of tech illiterate sheep. In Bud's mind the best of neo-reality wasn't to be found on the sterile corporatised mega-servers; but on the hidden, slow and steady underground networks. That was where the real business took place. Information and cash were the commodities of value in the dens of the Wired's most hidden venues.

Bud looked around at the immaterial locale that surrounded him. Europa-net, the massive government hosted network that acted as the digital centre of European society. It took the form of an impossibly clean city, populated by characterless globalised skyscrapers and futuristic superstructures. Each door on the Europa-net was a gateway to another server, another digital property made real by the Neuro-Network Protocol. Occasionally servers and whole realms went dark, falling into the metaphorical null undersea, slowly fading away only to be replaced by the next distinctly arranged array of bytes. A whole living, but not breathing world of electrons shifting, dancing, and shaping the future of the material world. An evolutionary ecosystem unconcerned with the limits of decay and physicality, simply the flow and progression of information. The most advanced self-programming program in the entirety of the world, re-writing itself by the minute as if by some unseen hand.

Before the Wired, there had been the Internet, a similar concept, but severely limited, only existing on the the screens of primitive computers. Many in those days saw the internet as the pinnacle of human achievement, they could only have dreamed of the Wired. In comparison, the Wired is far more visceral, real, and of course, addictive. For many it becomes more real than the real world. A better place, free from all the inconveniences, slights, and ugliness of flesh-space. To many the wired was an escape from physicality, with others, they found the better escape to be physicality. Both worlds existed in parallel, equally real, unequally physical. Both interacted with the mind in the same way.

In the distance Bud watched the crowds of people flowing in and out of the Free-Talk building. Free-Talk was one of the more popular social hubs with many different activities that could be rented for use with friends and strangers alike. To Bud it was the equivalent of a home for the mentally dull, a storage repo for all the lobotomised halfwitz to talk about their inane pleasures and pedestrian days. Bud didn't understand how people could live their lives in such a way, never exiting the metaphorical nursery.

Bud wasn't here for any of services on the consumer Wired though, Bud had jacked in for a very specific, highly illegal, and fairly dangerous reason. Tachiba Laboratories, a multinational megacorporation with ties to the European Secret Service, militaries all around the globe, and the technologies behind the Wired itself. The prime production facility of technological weapons used to bombard, constrict, and maim the free Wired wherever it could be found. Dedicated to the creation of a ``safe'' and ``secure'' mindrotting daycare for all of humanities overgrown children. Bud, deep in the stygian depths of the hidden Wired had overheard talk of a powerful and advanced piece of stolen software, just begging to be used by some ambitious computer cracker.

The software, nicknamed ``Tapper'' was designed for use by government or corporate surveillance operations, when burned onto the firmware chip of any consumer Neuro-translator it would allow the user to tap into the mind of any other user on the network. News about the Tapper was already spreading throughout the underground circles of the Wired, and there were many already desperately hunting for the elusive Crackers who had stolen it. Bud had heard from a close contact who went the by the alias Worm, that there were in fact only two Crackers, career types, in the market for profit rather than ideology. Not the types that Bud would usually associate with. They'd do anything for the right price, including double-crossing their ``friends''. The two who'd supposedly accquired the software from Tachiba were known for similar exploits in the past.

Two years earlier documents from Tachiba had begun to spread like wildfire, detailing extensive backdoors in the Neuro-Network Protocol. For weeks the identities of the leakers went unknown, moving like ghosts, leaving swathes of information in their wake. Eventually the leaker revealed himself, going by Balthasar; he had purchased the documents in bulk from the same two Crackers that Bud was now searching for. The two Crackers shared an alias, Serpent.

Despite being commercial Crackers they had become underground celebrities. Tachiba was a very high profile target; previously an uncrackable monolith, towering like an imposing sentinel, it's presence coating every corner of the Wired in it's poison. Now it's defenses, previously thought impregnable, had been breached. For months after the leaks, a veritable hoard of attacks battered the Tachiba networks each day. Only two made it through, and almost immediately realised the mistake they had made. The 26 Crackers involved in both attacks had found themselves within a mortal vice. Tachiba had set up a honeypot network. Each and every single one of the Crackers had their brains forcibly formatted to mental dust by their own Neuro-Translators. Their entire minds were erased like a hard drive; Tachiba had used one of the most vicious digital weapons known to man. The Crackers, while still alive, were a week later declared mentally dead, subsequently being euthanised. The mental formatting program was highly illegal, and the Cracker's families attempted to sue, but the case was thrown out. Tachiba faced no consequences for their use of the technology.

The Crackers very quickly became martyrs in the web of hidden networks, but little action was taken. No one wanted to become the next poor soul to get formatted.

Bud opened a virtual terminal. A rectangualar distortion took form infront of him, flowing like liquid crystal; it eventually formed into an opaque razor thin rectangle of frosted glass. The rectangle displayed a green blinking cursor, primed and ready for the slew of commands that Bud was about to load into it. Paired with the terminal was a similar virtual keyboard. Bud prepared to enter the hidden Wired, locking his trained fingers above the home row of the virtual keyboard. Then came a blindingly fast torrent of verbose commands each preparing the Neuro Translator for it's signal's forceful redirection into the void of the hidden Wired. Line after line slammed in, only pausing to wait for the command to finish it's execution. Bud targeted a server hosted off the coast of singapore, positioned just within international waters. A prime location to launch off the search he was about to begin.

The server switching command began it's countdown, 3, 2, 1, flight. Darkness, and then colour, floating surreal depictions of the Neuro-Network Protocol in action. Program logs flashing through the mind's eye, routing addresses appearing and disappearing in seconds, warnings, errors, and data all merging into a psychedelic stream of information within Bud's mental irreality. Slowly the stream slowed, and there was darkness once more. From the darkness then came form, shapes, colours, voices. The virtual terminal reappeared reporting a successful switch. Bud's view stabilised and he found himself within a vividly stylised technophilic temple.

Centred on the far wall of the temple, strung up by wires was a humanoid figure. It was assembled out of electronic parts and had been crucified on a set of oversized circuit boards. The head of the humanoid was a primitive beige display it's screen cracked; the display depicted a Lambda rendered in Ascii text. The closest thing to a religious symbol in the underground communities of Crackers. The Lambda has it's root in old computer science, when the art of cracking was young, and deeply rooted in mathematics. It was nod to tradition, and the foundations of Cracker culture in esoteric calculus.

The walls of the temple were lined with a living, breathing tangle of wires and electronica. Blinking lights, displays of all kinds, from all eras. Scrolling waves of thick green text rendered on black backgrounds. Out of this silicon sprawl, reaching into the ceiling like modern replications of ancient monoliths, were impossibly tall server racks, computers stacked on top of eachother as to reach some kind of digital heaven. A rhythmic humming filled the temple, like a choir, the warm sound of spinning fans and disks, interspersed with the occasional click or beep. From behind Bud came the sound of footsteps. Looking around he saw a feminine figure, wrapped in the garbs of one of the temple's maidens.

The outfit of the temple maiden was an impressive design, made out of a fabric that mimicked the properties of a computer display, it pulsed in mesmerising algorithmically perfect hypnotic patterns. The fabric was impossible, only the programmable irreal nature of the Wired allowed such a beautiful thing to exist. One of the many benefits of a world without physical limits. The woman in the garb was almost equally as beautiful, with model features, and deep soulful blue eyes. She had dark hair that ran down, her garb, illuminated by the colourful background. As she approached him, Bud executed a analysis program targeted at her. The analysis revealed that she was a program, an advanced one, designed with a limited artificial intelligence. She walked closer, and Bud stepped aside as she passed. For a moment he watched as she lit a small candle and placed it on a shrine below the crucified figure at the end of the temple.

Bud spoke, ``I'm looking for Priest. I have business with him.''. The maiden looked at him, like she was examining him. After a moment she spoke with a voice soft as a whisper in the night. ``You will find him outside, Your presence was expected.'' Bud nodded, and walked towards the massive industrial door that led to the outside. The doorway was painted a dull green, looking vaguely militaristic. The door was cracked open, letting in a stream of greyish sunlight. As he closed in on the door, he heard the crashing of waves, and could smell a tinge of salty air.

Bud pulled the heavy door open, and was met with the view of a grey sea, and crashing waves. He stepped onto the worn outcropping that looked out on the simulated endless digital ocean. Standing on the cliffside was a tall imposing figure. Wearing intricate pixel-woven robes and a regal though scrappy hat, was the man known as Priest. Some called him their prophet, others derided him as a cultist devoid of sanity. But there was no denying his reputation as a talented Cracker, and an influential man. As Bud opened his mouth Priest spoke his voice deep and commanding``You come in search of the Serpent. And you know that they have communed with me, with this I can surmise what has brought you here.'' Bud nodded. Priest spoke again ``The Wired connects all information, your visit is of no surprise.''. Bud paused for a moment before speaking ``Can you give me the information I need?'' Priest looked down, staring into the algorithmically simulated sea ``What you seek, you will use this to assault the temple of the corporate sciences, am I correct?.'' Bud nodded speaking affirmatively ``Yes.'' Priest gave a bittersweet smile, before continuing in an unusually somber and reverent tone ``You've heard the tales I assume, the beast within the mainframe, the dizzying inhuman unknowable structure of living data.'' Bud felt his heart jump ``You know I don't believe in that old Cracker lore. There's been talk of a killer ai roaming the wired for years, and it's never been true. Besides, the Turing convention forbids lethal AI.'' The words fell out of Bud's mouth fast, his true feeling's on the story spilling through his falsely confident tone. Priest looked deep into Bud's eyes ``The strings of the Wired ring with a consistent tone regarding it's existence, and those strings rarely reverberate falsely.'' Bud shook his head and decided to change subject ``So, where do I find the Serpent.'' Priest spoke ``You'll find them at the Golden Lambda, they've rented a private RAM host, the meeting will begin exactly at 3.41 AM Eastern European Time. If you miss it, the opportunity will be flushed.'' Bud nodded ``Alright, I'll be there. Tell them the meeting is on.''

It was a valuable piece of tech, especially for a ambitious Cracker like Bud. He had spent the previous 2 days trading and laundering obscene amounts of Digi-cash into three bank accounts located in South East Asia to prepare for the buy. He felt surprisingly nervous, possibilities of betrayal flashed as fast as they could through his virtualised mind. Bud began to execute the necessary scripts and programs to slingshot his digital consciousness into the hidden Neuro-network where he would complete the buy.

Multiple virtual terminals scrolled through text at unreadable speeds as his Neuro-translator was forcefully redirected into the hidden Neuro-network. The hidden network was far more resource constrained than it's normal counterpart, thus details were sparse. It took the form of a surreal dingy bar, black wires of all shapes and sizes coated the floor, linking a veritable treasure trove of computational devices. Blinking lights and terminals scrolling through esoterically dense program logs could be seen at every corner of the room, save for the bar itself. This specific instance of the network was named after the Greek God Dolos.

Bud could see two avatars at the far end of the bar, chatting amongst themselves. In the normal net, most peoples avatars were themselves, but on the hidden network, it was suicide to reveal ones flesh-space identity. Most people used a script to scramble their projected body into a vague anonymous shape of a human, more advanced crackers designed their own. The two crackers at the bar were taking the form of businessmen with beige CRT heads. The CRTs displayed a vomit of random pixels, most likely a visual dump of their systems RAM, it was a neat trick. Bud preferred a more minimalist avatar, he took the form of an ASCII body built out of random text scrambled from his system.

``You're here... Better not be a spook after all the trouble we've gone through.'' said the figure on the right. ``Have you got the Program?'' asked Bud, ignoring the comment. ``Of course. We assume you've brought the Digi?'' the figure on the left spoke, his voice reverberated throughout the room. ``I wouldn't be here if I hadn't.'' Bud said. ``You know how this works? 'Gardless, we wanted to warn you about somethin''' said the figure on the right. ``We discovered some bugs in our testing of the Program, signal interference seems, spooky stuff, voices that don't come from nowhere.'' Said the figure on the left. ``Any other bullshit you got for me?'' replied Bud. ``Jeez, it was just a warning man'' the figure on the right said. ``You ready to make the transfer?'' the man on the right said. ``Sure.'' Bud replied before summoning a virtual terminal in front of him. With a few commands, the funds funneled their way through eight nodes on a secure Digi-cash transport network. The two figures summoned a shared terminal and brought up an NFTP gateway. Neuro-File-Transfer-Protocol created a bridge between two Neuro-translators, the file was then encoded and sent through the senders brain to the receiver's. Bud accepted the transfer and felt the file being burned onto the partition in his mind that he had reserved for file storage, it was a large file, he didn't need a program to tell him that; the headache caused by the transfer was enough to tell. Once both parties had confirmed that the transfer had gone through they parted ways, with little in the way of goodbye.

Bud disconnected from the hidden network and spun up a self hosted private instance of the virtual environment. The private instance acted as a digital home of sorts. He had modeled it after an industrial apartment building, filled with programs as represented by physical objects. Bud summoned two virtual terminals, their impossibly thin screens hovered in space the environment behind them refracted and blurred allowing the text to be read cleanly. On one terminal he swiftly executed a file inspection command, targeting the compiled image of the Tapper. On the other he opened a text editor, and pointed it to the source code of the program. The program was written in Mentascript, a specialised language that was designed to interface easily with the Neuro-network protocol. For a Mentascript program it was incredibly dense, using a number of advanced features and custom modules. It attacked a vulnerability in the protocol that he hadn't seen before, injecting code into the signal from a user's Neurotranslator that rerouted what the user saw to a third party.

The file inspector measured the binary's space usage at 11 terabytes, relatively lightweight for a program of this capacity. The structure of the binary was unusual, probably compiled by a custom proprietary compiler. It would do the job, Bud thought. Bud had a target, and a good reason for buying this specific piece of software, he was going to turn it on it's creators.

The despisable Tachiba Laboratories were in Bud's eyes, and the eye's of the loose collective of Crackers, Cyber-Anarchists, and Technoheads, the Devil incarnate. They were known to be the worlds first and greatest supplier of invasive software, used by every digital snitch, spy, and Government spook on the Net. Bud had been for the past year been recruiting talented Crackers for an all out siege on the Tachiba Laboratories main network, the mysterious and nigh invincible ``Nephilim''. The Nephilim network was only accessible by Tachiba employees with a hashed 8192 bit authorisation chip specially implanted in the employees Neural-Expansion drive.

With some modifications to the Tapper program Bud was hoping to hijack and secretly copy the unencrypted access code to the Nephilim network as it was in transit to the authentication server. Bud spun up a secure NFTP gateway and sent the program, and source code to his 3 associates. A Cracker called Loosy, a systems engineer who went by Ryne, and a talented programmer who was known for some of the nastiest Mental-Malware on the wired. They had agreed to meet on a secure hidden network the following day to discuss how best to modify the program. In the meantime Bud had some work to do in the flesh-space, otherwise known as the real world.

The virtual apartment around Bud melted away into a black void, then. A tiny pinprick of white appeared, and then engulfed Bud's vision before the grim reality of flesh-space flooded in. Bud was lying on an uncomfortable bed, it was well used and stained heavily with sweat and coffee. The room around him didn't fair much better. The walls were a dirty industrial grey, worn from use and covered in small marks and dents. The room was illuminated by a single light and many monitors, just enough light to navigate through the maze of small gagdets, screens and devices scattered in a seemingly random pattern around the room. Next to the bed was the Neuro-translator used to jack into the Wired. It wasn't top of the line, but it did the job well enough. The computer powering the Neuro-translator was emitting a low hum, occasionally clicking; for Bud this was a strangely comforting sound. To the left of Bud was a doorway that led to the living room of the apartment.

Bud stood up. He rubbed his forehead, the headache from the transfer was still present, and probably would be for the rest of the night. On a small metal table by the side of the bed was a half empty mug of dark coffee. Bud picked up the grubby beige mug and swallowed the bitter liquid, hoping it would help alleviate the headache. Bud walked through the doorway on his left, hoping that maybe some food would maybe dent the headache. Before he got halfway a sudden rush of nausea hit him like a brick. Sickness was common after leaving the Wired. Bud lurched forward step by step, and shakily sat down on the grubby couch in the cramped living room. The table in front of the couch held a mess of digital magazines, empty snack packets, and the occasional box of pills. Bud groggily reached for the anti nausea pills he kept in reserve for occasions like this. Only one pill was left, but he gladly swallowed it. After a few minutes of uncomfortable silence, both the headache, and the nausea began to fade into the distance of a light opiate high.

As soon as Bud felt good enough to detach himself from the couch he moved toward the doorway that led out of his apartment. He grabbed a dark coat, he would need it for the cold night that awaited him outside of the relative warmth of his apartment. Inside the left pocket of the coat was a retractable knife, Bud gripped the small blade, and took a deep breath before opening the door and stepping outside. Bud's apartment was in the centre of one of the dodgier parts of the European Megacity he lived in. The megacity was situated roughly around the Rhine river. It stretched through the territories of 3 constituent nations of the European Collective, Luxemburg, The Benelux, and Germany. Bud was not a native, he had immigrated from The United States in search of new opportunities. He had a rough knowledge of the Dutch-German mix fusion that many of the inhabitants spoke.

The megacity had a different name for each border it was a resident in. Bud tended to just call it the Rine-stad. He lived in the Benelux portion of the megacity. The Rine-stad was one of 3 megacities belonging to the European Collective. Belonging was a strong word, as the cities were largely self governing. The apartment building Bud lived in was a depressing concrete monstrosity, built to house the overflowing population of the megacity. In the distance the lights of the Business and Shopping districts illuminated the night sky. Huge electronic advertisements could be seen even over the great distance, a testament to the willingness of corporations to pollute the even the heavens.

The district Bud lived in had far shorter buildings, but the advertisements and general sleaze was parallel. He locked the door behind him, and took the tired concrete stairs down to the ground floor. Sickly fluorescent lights coated the streets in a greenish palour. The streets were covered with long forgotten gum, and the cracked now empty containers of E-cigarette fluid. Darkened figures wearing black jackets walked past him, sometimes laughing, sometimes talking, sometimes whispering. It didn't matter to him.

The streets he walked through mostly looked the same. Only the vague shapes of neon signs reflected in puddles changing slightly. His destination was a grungy bar called Odium located on the far side of the district, known for attracting the ``wrong'' type of crowd. The bar came into view, it's neon sign was a fish holding a beer bottle, while smiling and winking. The Odium stank of smoke and piss. Nevertheless Bud walked in, keeping his head down. He spotted his target, Franz Odessa. Franz was a strange man, balding in all the wrong places, and with a constant grin, that would be reassuring if it wasn't for his chemically stained teeth. Despite this grisly appearance Franz wore clean, and well taken care of clothing. Franz was a chemical wizard, and could cook up the perfect cocktail for any occasion. Bud needed a Mental-enhancer, something to boost his clock to prepare for the coming days, and Franz was his man. They hacd a history, Franz dabbling in some smalltime cracking himself. It was often a mutually beneficial relationship, Bud got his chemicals for a reduced price, and Franz had his competition eliminated. Bud knew Franz would be at The Odium, he always was.

The Odium, like most places in the district was cramped. Gaggles of young people stood in different groups, some enjoying their drinks, others deep inside the void of chemical bliss. The bartender had a mechanical arm, one of the better models, certainly not cheap. Bud had heard from Franz that he was an Ex-mercenary, fought in the Congolese Civil War. Which one, Franz didn't know.

Bud waved at Franz from across the room, catching his attention. He then walked over to where Franz was standing at a dingier than usual part of the bar. Franz cracked a hideous grin, a practice he knew well made people uncomfortable. ``What'll it be tonight, Cowboy.'' he said, maintaining the unsettling grin. ``Need an enhancer, something that'll keep me on the game for a while.'' Bud replied not missing a beat. ``Important job? I like to think I've got the perfect thing my friend.'' said Franz, somehow making his grin even more unbearable. ``I need it now, jobs soon, can't mess it up.'' Bud replied, averting his eyes from Franz. Franz reached deeped into his dark green coat, he pulled out a small plastic box, and carefully slid the lid off. Inside was a baggy of 12 or so pills. ``These are what you're looking for. Fuck feeling in the zone, this stuff'll make you feel like you ARE THE ZONE.'' Franz said with an uncomfortable enthusiasm. ``How much?'' Bud asked as he inspected the pills. ``15k in Digi-cash'' Franz said eagerly. ``It'll be in your account by the end of the week.'' Bud said, snatching the box, and swiftly placing the plastic lid back on. ``It's your problem if it isn't. Enjoy it Cowboy.'' Franz said with a chuckle. Bud nodded and slid the rough plastic box into his coat. As he left the bar, he noticed a man watching him from a table in the back. The man's face looked warped, possibly a botched cosmetic surgery, or some form of facial reconstruction. Bud felt uneasy, and avoided the man's gaze. He pulled his coats hood over his face and left The Odium. With the pills in his pocket, Bud let his mind drift to the job.

He imagined his associates were already working on modifying the Tapper for auth hijacking. The target would have to be an employee at Tachiba with the right access, but not smart enough to protect themselves from being bugged. When they were in the system it wouldn't take long for a network master to find them and de-auth them, they'd have to be fast. The goal, thankfully was simple, get in, copy as much as possible, format everything, get out. As Bud approached the apartment building he found himself staring at the flaking red paint covering it, he wondered what the building would have looked like while new. What hopes did it's original inhabitants have? The sickly green lights of the stairwell leading up to his floor greeted him. As he stood infront of the metal door that acted as a gateway into his home, he thought about the man in the bar. Who was he? Bud thought maybe his paranoia was getting to him. He opened the door to his apartment, and it made a terrible screech as it slid open.

Once inside he found his way to his bed, and after a few minutes fell into an uncomfortable sleep, filled with stray thoughts and anxieties from the day. Some were about the job, others about the man in the bar. His mind was restless even in the solace of sleep.

\chapter{''bitfall''}
Bud attached the black plastic connector into the implant on the side of his head that allowed him to access the Wired Network. It made a satisfying click, and he heard a whirr from the computer he was now attached to. Before activating the connection and entering the Wired; Bud opened the black plastic box he had received the previous night and carefully removed a singular pill, he swallowed it, and washed it down with a bitter gulp of lukewarm coffee. It started as a buzzing, a rush of energy and alertness, slowly filling his mind, every detail seemed important, every connection visible and clear. He shuddered at the feeling, and then without hesitation flipped the black switch on the aging computer beside him, entering the Wired.

A feeling of falling, strange voices, garbled audio, colours flashing. The bright digital city of the wired fell into view, it's alleyways, tunnels, and highways illuminated in a beautiful mesh of vectors textures and precise programming. To Bud, the wired felt more real than flesh-space. It felt like home. Bud ground his teeth, and opened a virtual terminal, sending commands flying into the black and green coloured shell, a cornucopia of text flashing back in digital response. ``:> exec: NNC targ = **@333:55:09:AAB:3@:9T9'' He felt as his conscious mind was ripped from the corporate themepark of the consumer Wired to the underground hive of the Hidden Network. He watched the surreal abstractions of data fly past him, intense colours, untold structures, and megaliths of digital noise, all floating in endless simulated black void. Then he arrived. The Dolos, where he had purchased the Tapper, they had agreed to meet here.

Bud had arrived first, but the others were not far behind him. Second to arrive was Loosy; her avatar was a loose collection of wet primitively rendered blobs of colour floating gravityless. Next was Ryne, he didn't have an avatar, just a generic scrambled Human. Finally John arrived, he never was one for fancy aliases. His avatar was as generic as his name, an unassuming cartoonish man in a semi-casual business outfit. Bud visualised a table and some chairs, and the group sat down. ``I took a look at the Tapper, it's quite a piece of tech. I haven't seen such an advanced use of Mentascript coming out of Tachiba in a long time.'' John said. ``I made some simple modifications to it after reversing engineering a chunk of the API, I can have the prog ready by Tomorrow.'' John continued, sounding confident.

\chapter{''END''}
``There's something coming through the mainframe!''
\end{document}
